Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-06-03 talk/dls2014/paper/paper.tex
Tweaks

Obviously, if we are in a shared-memory setting, this model is extremely
wasteful: at a given time, most objects are identical in all, or most,
segments.  They differ only in segments that have modified but not yet
committed the object.  So we use a trick of the Memory Management Unit
(MMU) of the CPU.  At the coarse unit of one page of memory (4096
bytes), we use remappings so that, in general, pages within segments are
\emph{shared} with each other if they would contain a fully identical
copy.  Conversely, when one segment needs to write to one object
contained in a page, the complete page is first \emph{privatised}: it is
duplicated and the copy is remapped so that it will be visible in this
segment (only).  This process is illustrated in
figure~\ref{fig:Page-Remapping}.

@@

This area can be seen as a continuous array of bytes that is indexed
from the start of the segment by an object's reference ($SO$) divided
by 16 (this requires objects to have a size which is dividable by 16).
Instead of just setting the byte to \lstinline!true!  if the
corresponding object was read, we set it to a \lstinline!read_version!
belonging to the transaction, which will be incremented on each
commit.  Thereby, we can avoid resetting the bytes to
\lstinline!false!  on commit and only need to do this every 255
transactions. The whole code for the barrier is easily optimisable for
compilers as well as perfectly predictable for CPUs:

>>>>

Obviously, if we are in a shared-memory setting, this model is extremely
wasteful: at a given time, most objects are identical in all, or most,
segments.  They differ only in segments that have modified but not yet
committed the object.  So we use a trick of the Memory Management Unit
(MMU) of the CPU.  At the coarse unit of one page of memory (4096
bytes), we use remappings so that, in general, pages within segments are
\emph{shared} with each other if they would contain a fully identical
copy.  Conversely, when one segment needs to write to one object
contained in a page, the complete page is first \emph{privatised:} it is
duplicated and the copy is remapped so that it will be visible in this
segment (only).  This process is illustrated in
figure~\ref{fig:Page-Remapping}.

@@

This area can be seen as a continuous array of bytes that is indexed
from the start of the segment by an object's reference ($SO$) divided
by 16 (to avoid false conflicts, all objects have a size of at least 16 bytes).
Instead of just setting the byte to \lstinline!true!  if the
corresponding object was read, we set it to a \lstinline!read_version!
belonging to the transaction, which will be incremented on each
commit.  Thereby, we can avoid resetting the bytes to
\lstinline!false!  on commit and only need to do this every 255
transactions. The whole code for the barrier is easily optimisable for
compilers as well as perfectly predictable for CPUs:
